\mireval{}:\\ A Transparent Implementation of Common MIR Metrics

### 2014-07-04 paper/paper.tex
Added dpwe NSF acknowledgement.
added cusp affiliation
New ISMIR paper template ughhh
Update paper.tex
put line break in title; added in part to NSF support claim

% -----------------------------------------------
% Template for ISMIR 2014
% (based on earlier ISMIR templates)
% -----------------------------------------------

\documentclass{article}
\usepackage{ismir2014,amsmath,cite}
\usepackage{graphicx}
\usepackage{dsfont}
\usepackage{stmaryrd}
\usepackage{braket}
\usepackage{authblk}
\usepackage{booktabs}

@@

\title{\mireval{}: A Transparent Implementation of Common MIR Metrics}

@@

\author[1]{Colin Raffel}
\author[1]{Brian McFee}
\author[2]{Eric J. Humphrey}
\author[2]{Justin Salamon}
\author[2]{Oriol Nieto}
\author[1]{Dawen Liang}
\author[1]{Daniel P. W. Ellis}
\affil[1]{LabROSA, Dept. of Electrical Engineering\\Columbia University, New York}
\affil[2]{Music and Audio Research Lab\\New York University, New York}

@@

The authors would like to thank Matthew McVicar for helpful advice about comparing chord labels.

>>>>

% -----------------------------------------------
% Template for ISMIR Papers
% 2014 version, based on previous ISMIR templates
% -----------------------------------------------

\documentclass{article}
\usepackage{ismir,amsmath,cite}
\usepackage{graphicx}
\usepackage{dsfont}
\usepackage{stmaryrd}
\usepackage{braket}
\usepackage{authblk}
\usepackage{booktabs}

@@

\title{\mireval{}:\\
A Transparent Implementation of Common MIR Metrics}

@@

\author[1]{Colin Raffel}
\author[1]{Brian McFee}
\author[2]{Eric J. Humphrey}
\author[2,3]{Justin Salamon}
\author[2]{Oriol Nieto}
\author[1]{Dawen Liang}
\author[1]{Daniel P. W. Ellis}
\affil[1]{LabROSA, Dept. of Electrical Engineering\\Columbia University, New York}
\affil[2]{Music and Audio Research Lab\\New York University, New York}
\affil[3]{Center for Urban Science and Progress\\New York University, New York}

\def\authorname{Colin Raffel, Brian McFee, Eric J. Humphrey, Justin Salamon, Oriol Nieto, Dawen Liang, Daniel P. W. Ellis}

@@

The authors would like to thank Matthew McVicar for helpful advice about comparing chord labels.  Support provided in part by NSF grant IIS-1117015.
